## Function + Environment = "*closure*" {style="margin:10px;font-size:80%;"}

Functions are containers for R code.^[There are others, see `quote()`, `expression`, and `parse`.]

<div class="container">
<div class="col">
Constructing functions

- usually, the container is created by the keyword `function`
- **arguments** are in parentheses.
- R code placed in the curly brackets defines the **body** of the function.
    - The code in the body is **not evaluated** when the function is constructed.
- A reference to the **environment** in which the function was created is carried along with the function.
</div>
<div class="col">
Evaluating functions

1. Create an environment that binds values to the argument names.
2. The parent of this environment will be the one carried along with the function.
3. Run the code in environment (1) (which provides access to the parent environment)
4. Erase environment (1) but **return** a selected object as the **value** of that function. 

</div>
</div>

## Your turn: Components of a function

In your console, create some R function with three arguments and two lines of code. Bind it to the name `my_function`.

Access the three components individually with:

- `formals(my_function)`
- `body(my_function)`
- `environment(my_function)`

What is the `class` of each of these components?

What do these computations return?

- `all.names(body(my_function))`
- `all.vars(body(my_function))`

## Persistent storage by functions {style="margin:0px;font-size:80%;"}

Often, especially in Shiny, a function will make reference to objects that remain extant between calls to the function.

- In some languages, not R, there is something like a `static` or `persistent` declarative that creates persistent storage.
- Beginning programmers often create objects in the Global environment that will be available to any function to access and mutate.
    - This is a risky technique. Functions that you've never heard of my alter the persistent objects in any way whatsoever.
- In R, reliable persistent storage is often created by exploiting the function creation system. This technique uses `function()` within the body of another function.

## Example: a counter {style="margin:0px;font-size:90%;"}

```{r}
make_counter <- function(start = 0) {
  val <- start
  list(
    incr = function() {val <<- val + 1},
    decr = function() {val <<- val - 1},
    reset = function(start = 0) {val <<- start},
    value = function() val
  )
}
```

```{r}
cars <- make_counter()
trucks <- make_counter()
cars$incr(); cars$incr(); trucks$incr(); cars$incr()
cars$value()
trucks$value()
```

## Other ways to capture unevaluated code

```{r}
my_code <- substitute(x <- 17)
bigger_code <- substitute({
  x <- 23
  y <- 44
})
```

The `<rlang>` package offers another system for doing this.

## Your turn:

```{r}
my_code <- substitute(x <- 17)
bigger_code <- substitute({
  x <- 23
  y <- 44
})
```

1. Enter the above assignments in your console.
2. What are the values of `x` and `y` *afterward*?
3. Try `class()` and `all.vars()` on `my_code` and `bigger_code`
4. Run `eval(my_code)`. What are the values of `x` and `y` now?
5. Run `eval(bigger_code)`. What are the values of `x` and `y` now?


## Back to the Knight Bus

Shiny uses this technique in its "server" function.

```r
knight_bus <- function(input, output, session) {
  f1 <- function() {
    input$button == 10
  }
}
```

The function `f1` knows to look to it's birth environment for the value of `input`.

`shinyApp()` sets this up.
