## Dashboards

```{r include=TRUE}
library(shiny)
library(flexdashboard)
```



## Preliminaries

Nota Bene: The RStudio viewer does not display dashboards correctly. So use a web browser.

If  your target is not a "normal"-size display (technical: 768 pixels or more in height), use the browser in emulation mode.
     - In Chrome, CMD-OPT-I brings up the console.

## [Flexdashboard](https://bookdown.org/yihui/rmarkdown/dashboards.html)



Set things up in YAML:

```
---
title: "Dashboard Value Boxes"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    navbar:
      - { title: "About", href: "https://example.com/about" }
      - { title: "StatPREP", href: "https//statprep.org"}
---
```

## Layout

The navbar is described in the YAML. But everything else is ordinary headings.

`flexdashboard::flex_dashboard()` is an R/Markdown renderer that treats headings specially.

- *First Level* (`#`) -- a page 
    - navigation menu with buttons for each tab
    - button label is text of header
    
    
- Second Level (`##`) -- a row in a page. (Note: because YAML specified `orientation: rows`. Default is columns.)
    - header text doesn't matter

- *Third level* (`###`) -- a box in a row
    - header text becomes a label, maybe integrated into a widget.


## Attributes

- First level: (`#`)
    - use `data-icon=fa-umbrella` attribute to set logo (if any). Note: `fa-` prefix is used, unlike with the `icon()` function in Shiny.

- Second level: (`##`)
    - A narrow column `{data-width=350}`
    - Third-level elements should be in tabs: `{.tabset}`


## Value boxes

```{r eval = FALSE}
spam <- 17
valueBox(
  spam, icon = "fa-trash",
  color = ifelse(spam > 10, "warning", "primary")
)
```

## Icons from [Font Awesome](https://fontawesome.com/icons?d=gallery&m=free)

1500+ free icons

`r icon("anchor")`   `r icon("angry")`   `r icon("ankh")`  `r icon("balance-scale")`   `r icon("band-aid")`   `r icon("battery-half")`    icon("credit-card")`   

## Valid statuses

Essentially, a small library of colors intended to be use symantically:

- `primary` Blue (sometimes dark blue)
- `success` Green
- `info` Blue
- `warning` Orange
- `danger` Red



## Another dashboard format: `<shinydashboard>`

Unlike flexdashboards which is based on markdown, shinydashboard is based on the html-based construction kit that we used in  `fluidPage()`, etc.

New elements:

- Top level: `dashboardPage()`
- Next level: 
     - `dashboardHeader()`
     - `dashboardBody()`
     - `dashboardSidebar()`

- Containers
    - `fluidRow()`
    - `dropdownMenu()` holds
        - `messageItem()`s: from, message, icon, time, href
        - `taskItem()`s: text, value, color, href
        - `notificationItem()`s: text, icon, status, href
     
- Potentially recursive structures
    - `box()` -- a container based on Bootstrap 12-grid
        - can be collapsed
    - `tabBox()` -- contains `tabPanel()`s

- Terminal elements (aka "leaves)
    - `valueBox()`, `valueBoxOutput(id)`, `renderValueBox(valueBox())`
    - `infoBox()`, `infoBoxOutput(id)`, `renderInfoBox(valueBox())` 




##  Another format: [Storyboards](https://bookdown.org/yihui/rmarkdown/layout.html#story-boards)

I don't see many of these, but they are straightforward. 

YAML:

```
---
title: "A Walk through Wonderland"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---
```
 
## Storyboard items

- Each item is a third-level header (`###`)
- The header text becomes the content of the board
- The content becomes the big display associated with that board
- Optionally, a `---` produces a side display

Example: `Projects/Project-5-dashboards/storyboard.Rmd`
