---
output: 
  revealjs::revealjs_presentation:
    self_contained: false
    reveal_plugins: ["notes", "search", "chalkboard", "menu"]
---

```{r child="page-definitions.Rmd"}
```
 
#   {data-background-image="./images/title-slide.png"}
 
# Orientation  {data-background-image="./images/cityscape.png"}

---

1. Outline
2. People
3. Computer setup
4. The workshop proper


# Outline 

```{r child="schedule.Rmd"}
```

# People

```{r child="people.Rmd"}
```

#   {data-background-image="./images/sticky-notes.png"}

#   {data-background-image="./images/workshop-policies.png"}

# Computer Setup

```{r child="computer-setup.Rmd"}
```

# File Organization

```{r child="file_organization.Rmd"}
```

# What is a shiny app?

```{r child="what-is-an-app.Rmd"}
```





# An introductory app {data-background-image="./images/cityscape.png"}

```{r child="project-0.Rmd"}
```


# Building a UI {data-background-image="./images/cityscape.png"}

## Three conceptual levels

It's helpful to divide the ideas behind implementing a UI into three conceptual levels.

1. Instantiating input and output widgets
2. Frameworks for layout
3. Organizing *within* framework elements


# Widgets

```{r child="widgets.Rmd"}
```

# Project 1

```{r child="project-1.Rmd"}
```

# Frameworks & Layouts

```{r child="UI-frameworks.Rmd"}
```

## Project 2

```{r child="project-2.Rmd"}
```

# Reactives {data-background-image="./images/cityscape.png"}

```{r child="closures.Rmd"}
```

```{r child="reactives.Rmd"}
```

# Project 3: Plot a data frame

```{r child = "project-3.Rmd"}
```



# Debugging 

```{r child="debugging.Rmd"}
```


# Project 2 return
 
## Augment the server for Project-2-calculator

# Avoiding reactive loops: Updating inputs

```{r child="values-and-inputs.Rmd"}
```

# Project 3: server components


```{r child = "project-3.Rmd"}
```



# Shiny documents

<!-- Laying out an Rmd document: Big Mac?

See prototype.Rmd under 06-design-ui
-->

# Dashboards

```{r child="dashboards.Rmd"}
```

# TUESDAY {data-background-image="./images/title-slide.png"}

# Deploy

```{r child="deploy.Rmd"}
```

# Learnr tutorials

# Persistent storage

```{r child="persistent.Rmd"}
```

# Prettifying your app

```{r child="prettifying.Rmd"}
```



# Shiny Modules {data-background-image="./images/cityscape.png"}

## Motivation

Do Task 1 in `project-4-modules.html`. 

This will set us up for understanding Shiny modules.


```{r child="modules.Rmd"}
```

# Project 4

```{r child="project-4-modules.Rmd"}
```
