```{r  include=FALSE}
library(shiny)
library(dplyr)
library(ggplot2)
library(DT)
```

# Writing our First App

A simple app written in an unconventional way.

It may look strange if you have already written Shiny apps.

Meant to demonstrate the  full scope of app writing in a compact example.

File in directory "Projects/Project-0"

## The file, `app.R`  {style="color:blue;"}

Everything is in this one file, but there's no requirement for that. 

Alternatives:

- separate `.R` files for the various components, sourced into `app.R` 
- functions provided by a package
- mix and match

## `app.R` is an ordinary R script

You can run in  the normal ways, e.g. cmd-p, source-button, ...

Because of the call to `shinyApp()` (last line), the  RStudio IDE gives you a "Run" button. 

But you can work with this file outside of RStudio if you wanted to.


## Start in the Muggle world {style="margin:0px;font-size:80%;"}

<div class="container">
<div class="col">

```{r echo=TRUE}
## Muggle World
library(shiny)
library(dplyr)
library(ggplot2)
library(DT)

muggle_plot <- function(xvar, yvar) {
  ggplot(
     diamonds %>% sample_n(size = 200), 
     aes(x = !!xvar,  y  = !!yvar)) +
  geom_point()
}

# test for Muggle functionality:
# muggle_plot(as.name("cut"), 
#             as.name("price"))
```
</div>
<div class="col2">
- Ordinary package  loading  with `library()`, then
- Defines a function, `muggle_plot()`.
     - since it's in the Muggle world, it's a perfectly ordinary function with arguments. 
     - I  wrote it as a function because I know what's coming.
</div>
</div>
 
- Even simple functions can be subtle (e.g. the `!!xvar`),  so be sure to test and  debug it in the Muggle world.

**Your Turn**: Evaluate the first several lines of `app.R`, then run the test of `muggle_plot()`.

## Specifications for User Interface {style="margin:0px;font-size:80%;"}

<div class="container">
<div class="colsmall">
```{r echo = TRUE}
user_interface <- tagList(
  h2("A very basic Shiny App"),
  p("This app demonstrates the split 
    between the Muggle and Wizard worlds"),
  actionButton("go", "Go!"),
  plotOutput("main"),
  textOutput("button_message")
)
```
</div>
<div class="col4">
- The functions `tagList()`, `h2()`, and `p()` are from the `<htmltools>` package.
- They are perfectly ordinary functions. They generate HTML -- essentially a character string.
- The functions `actionButton()`, `plotOutput()`, and `textOutput()` are from the `<shiny>` package and are also  perfectly ordinary functions. They also generate HTML.
</div>
</div>

**Your turn**: At the console, run one or more of the individual lines  in the user interface. What does the result look like?

## The bridge from the Wizard world to the Muggle world {style="margin:0px;font-size:80%;"}

I'm calling it `reactive_logic` but it's usually called "server".

<div class="container">
<div class="col">
```{r echo=TRUE}
reactive_logic <- function(input, output, session) {
  output$main <- renderPlot(
    muggle_plot(as.name("cut"), 
                as.name("price"))
  )
  output$button_message <- renderText(
    paste("You have pressed the button", input$go, 
          "times.")
  )
}
```
</div>
<div class="col3" style="font-size:90%">
- arguments are always `input,  output, session`
- the contents look  ordinary, but  they  are highly stylized:
    - assignments  to `output[[`*name*`]]`
    - calls `<shiny>` functions such as `render___()`. Others we will see: `observe()`, `react()`, `isolate()`, ...
</div>
</div>

**Your turn**: At the console, run `renderText("hello")`. What's the value of this expression? Are their side effects?

## Invoking the app {style="margin:0px;font-size:80%;"}

<div class="container">
<div class="col">
A simple function call:

```r
shinyApp(user_interface, reactive_logic)
```

**Your turn**: Run it in  the console.
</div>
<div class="col">
Uses the  objects we created: `user_interface` and `reactive_logic`.

**Your turn**:

- What kind of objects are `user_interface` and `reactive_logic`?
    Hint: Use `class()`
- What kind of object is produced by `shinyApp()`?
    Hint: Name the object `hoo <-` and  look at the `class()`. Then  "print" it.
</div>
</div>


## Modify the App

Just to get an idea of what you already know.

**Your turn**:

1. Don't display the button message until the button value is > 2.
2. Add `selectInput()`s for the x-variable and y-variables.
3. (Aspirational) Connect the x- and y-selectors to the plot. **Nota Bene: We haven't yet covered how to do this.**

## Deploy the app

With the `app.R` file open  for editing, press "Run App"

You will be asked to set up some things  relative to your `ShinyApps.io` account.

**Your turn**: Try to deploy the app. If you  succeed, you can be a resource for your neighbor who didn't have such good luck.

If you don't succeed, ask a TA for help during a break. We're moving on and will return  to deployment tomorrow.
