---
title: "Project 2: Calculator"
---
```{r child="../../page-definitions.Rmd", eval=not_child}
```

```{r  include=FALSE}
library(shiny)
library(dplyr)
library(ggplot2)
```

```{r child="../../page-definitions.Rmd", eval=not_child}
```

## Project Four: Calculator 

In the `Projects/Project-4-Calculator` directory are several files. 

We'll start with `app.R` and `keyboard.R`.

## Phase I: Extend the UI

1. Confirm that you can run `app.R` to create a UI as might be suitable for a calculator.
2. Glance through the functions in `keyboard.R` to get an idea of how you might add new keys. (Hint: It's not hard.)
3. Add several keys: square-root, exp,  ln, sin, .... Keep in mind, these keys don't have to do anything yet except allow themselves to be pushed.

## Phase II: Start writing the server

The file `server-starting.R` contains statements that call some of the Shiny functions to create reactives. These statements will be `source()`d into the `server()` function, as if they were typed there.

To start the server:

1. Create a reactive value `entry_string`. This will store the number being created at the keyboard. Initialize it to a blank string: `""`.
    - which of the Shiny functions to make reactives will you use?
2. Arrange that the value of `entry_string` is at all times displayed in the `current` UI output widget.
    - which of the Shiny functions to make reactive displays will you use?
3. Write an observer which, when the "one" button is pressed, concatenates a "1" to the `entry_string`. 
    - Use `observeEvent()`.
4. Write similar observers for the other 11 buttons in the 4x3 array of keyboard buttons.
    - the tricky one is for "delete". `substr()` and `nchar()` will help.

## Phase 3: Respond to the operation buttons

The file `server-ops.R` is intended to hold server commands to handle the operation  button presses. It's blank right now. 

Your task is to implement a system that will determine which operation button was pressed and store a corresponding identifying string in the reactive value named `last_op`.

## When `last_op()` changes

## Your Turn: Taking an action when `last_op` changes

Read through `server-ops-soln.R` to see some ideas.

1. Make a note of what doesn't make sense to you or why one reactive constructor is used rather than another.
2. Let's discuss and play with changes as they come up.

## Changes that don't register

In `server-ops-soln.R` on lines 18, 20, 22, and so on, what's going on? Why is `last_op()` being called twice, when only the second call really matters? What happens when the first call is deleted?

Hint: 3 + 2 + 4





## See what happens if we change observeEvent to observe

Talk about isolate.


