---
title: "Exploratory report"
author: "Daniel Kaplan"
date: "1/27/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
library(dplyr)
library(shinyjs)
data("SaratogaHouses", package = "mosaicData")
knitr::opts_chunk$set(echo = TRUE)
```




```{r echo=FALSE}
price_filter <- 
  sliderInput("price", "Price range (K)",
              min = 0, max = 500, value = c(0,500),
              step = 1)
lot_area_filter <- sliderInput("lot_area", "Lot size (acres)",
                               min = 0, max = 5, value = c(0,5),
                               step = 0.1)
bedrooms <- sliderInput("bedrooms", "Bedrooms", min = 0, max = 10, 
                       value = c(0,10))
construction <- selectizeInput("construction", "Construction",
                               choices = c("new", "old"),
                               selected = "new")
```


In response to your recent query, here is the report on real-estate transactions over the last year. Altogether, there were `r nrow(SaratogaHouses)` sales.

criterion  | acceptable values
-----------|------------------
`r checkboxInput("by_price", "By price")` | `r price_filter`
`r checkboxInput("by_lotsize", "By lotsize")` | `r lot_area_filter`
`r checkboxInput("by_bedrooms", "By number of bedrooms")` | `r bedrooms`
`r checkboxInput("by_const", "By construction")` | `r construction`

`r textOutput("n_satisfying", inline=TRUE)` houses meet your criteria. 

The median price is $`r textOutput("median_price", inline=TRUE)`.

## Reactive logic tasks

1. Write reactives that, given the selection criteria, filter the `SaratogaHouses` data frame to produce just those rows meeting the criteria.
    - You may want to implement just one of the criteria before adding the others.
    - Think about whether you want just one reactive that does all the filtering, or a series of reactives each of which filters the output of the previous reactive according to an additional criterion.
2. Fill in the `textOutput()` named `"n_satisfying"` with the number of rows in the filtered data.
3. Fill in the `textOutput()` named `"median_price"` with that numerical value
4. There are checkboxes for the criteria. Arrange things so that, when unchecked, the corresponding slider/selector disappears and that criterion is not used for filtering.
    - here, we'll use a UI modifier, `conditionPanel()`
    - In a script-file app, you could use functions from the `shinyjs` package, `hide()` and `show()` to determine whether the widget is being shown. For instance, `hide("price")` will hide the widget with the id `"price"`.
5. When you have things working, move the UI and reactive logic into an `app.R` style of app.
    - The point here is better to understand the organization of components in `app.R`.
    - Also, it's easier to debug in an `app.R`.

For those of you without `dplyr` experience, here is a statement that will take two values defining a range, `lower` and `upper`, and return just those rows where `price` is in the range.

```{r}
lower = 100000
upper = 150000
Acceptable <- SaratogaHouses %>% 
  filter(price >= lower, price <= upper)
```

`Acceptable` will be a data frame with just the houses that pass the test.

```{r child="soln.Rmd", eval=FALSE}
```